\TheTitle

### 2017-07-13 paper/study.tex
Fixing study parts (part 1 of many)
Adding null hypotheses to summarization study.

Adding statistical results for Cross-commit and Correctness.
Fixing the correctness metrics to be split for T5 and T9.

The accuracy metrics are measured slightly differently between tasks due
to different requirements and structures in the answer. In task T4, both
the order and the merges are important. We define the distance to be the
edit distance with insertion, deletion, and transposition at unit cost.
The accuracy is the minimum edit distance necessary to make the answer
correct. T5, T9, and T10 are concerned with the set of elements in the
response; the order is not important. We use the Levenshtein distance,
with insertion, deletion, and substitution of unit cost, from the
provided answer to the correct answer. The answers to T6 and T8 are
single number values; the distance is measured as the absolute value of
the difference between the provided answer and the correct answer. T7
has only a single correct answer, thus the distance would either be zero
or one. For this reason, it is acceptable to omit the accuracy metric
from this task. The correctness metric is simply whether the answer was
correct or not; an accuracy of zero indicates a correct answer.

@@

% TODO: Add the null hypotheses for each question to the procedures
% TODO: Include the Wilcoxon Test and Cliff effect size test results

The results show ( Figure~\ref{fig:summarization_results} ) that in all
cases, except for T10, the number of instances of a correct result with
\tool is roughly the same as the number of incorrect instances with
gitk. \tool outperforms Gitk in correctness by a large margin. We use
the McNemar Chi-square test~\cite{McNemar1947} with continuity
correction to test the statistical significance of the hypothesis that
\tool improves the correctness of the participants. We use $\alpha =
0.05$, or a $95\%$ confidence level, therefore the $\chi^2$ test
statistic is 3.841.

\begin{figure*}[htpb]
  \centering
  \includegraphics[width=\textwidth]{figures/userstudy/results.pdf}
  \caption{Results from the summarization tasks. The first row plots the
    correctness metric for each task. The second row plots the
    accuracy metric for each task. The third row plots the time metric
    for each task.}
  \label{fig:summarization_results}
\end{figure*}

\begin{table}[htpb]
  \centering
  \caption{Correctness Results}
  \label{tab:correctness_table}
  \begin{tabular}{crrc}
    \toprule
    Task & $\chi^2$ & $p$-value & Conclusion\\\midrule
    T4   & 13.07    & 0.0003    & Reject $H_0$\\
    T5   & 12.07    & 0.0005    & Reject $H_0$\\
    T6   & 14.06    & 0.0002    & Reject $H_0$\\
    T7   & 11.07    & 0.0009    & Reject $H_0$\\
    T8   & 13.07    & 0.0003    & Reject $H_0$\\
    T9   & 12.07    & 0.0005    & Reject $H_0$\\
    T10  & 4.00     & 0.0455    & Reject $H_0$\\
    \bottomrule
  \end{tabular}
\end{table}

The results for the correctness metric are summarized in
Table~\ref{tab:correctness_table}; the full results are as follows;

@@

@@

    T4; The $\chi^2$ statistic is $13.07$ with a p-value of $0.0003$.
    $13.07 > 3.841$ and $0.0003 < 0.05$, therefore we reject the null
    hypothesis.

@@

    T5; The $\chi^2$ statistic is $12.07$ with a p-value of $0.0005$.
    $12.07 > 3.841$ and $0.0003 < 0.05$, therefore we reject the null
    hypothesis.

    \begin{tabular}{cc|rr}
                            &           & \multicolumn{2}{c}{Linvis}\\
                            &           & Correct                      & Incorrect\\\hline
      \multirow{2}{*}{Gitk} & Correct   & 5                            & 0\\
                            & Incorrect & 14                           & 4\\
    \end{tabular}\\

@@

    T9; The $\chi^2$ statistic is $12.07$ with a p-value of $0.0005$.
    $12.07 > 3.841$ and $0.0005 < 0.05$, therefore we reject the null
    hypothesis.

    \begin{tabular}{cc|rr}
      &           & \multicolumn{2}{c}{Linvis}\\
      &           & Correct                      & Incorrect\\\hline
      \multirow{2}{*}{Gitk}  & Correct   & 6                            & 0\\
      & Incorrect & 14                           & 3\\
    \end{tabular}

>>>>

The accuracy metrics are measured slightly differently between tasks due
to different requirements and structures in the answer. In task T4, both
the order and the merges are important. We define the distance to be the
edit distance with insertion, deletion, and transposition at unit cost.
The accuracy is the minimum edit distance necessary to make the answer
correct. T5, T9, and T10 are concerned with the set of elements in the
response; the order is not important. We use the Levenshtein distance,
with insertion, deletion, and substitution operations of unit cost, from
the provided answer to the correct answer. The answers to T6 and T8 are
single number values; the distance is measured as the absolute value of
the difference between the provided answer and the correct answer. T7
has only a single correct answer, thus the distance would either be zero
or one. For this reason, it is acceptable to omit the accuracy metric
from this task. The correctness metric is simply whether the answer was
correct or not; an accuracy of zero indicates a correct answer.

Statistical significance testing is performed to verify that the results
are meaningful. We use $alpha = 0.05$ or a $95\%$ confidence level. The
McNemar $\chi^2$ test\cite{McNemar1947} with continuity correct is used
to test the statistical significance of the hypothesis that \tool
improves correctness of the participants. The $\chi^2$ threshold
statistic at $\alpha = 0.05$ is 3.841. The Wilcoxon\cite{Wilcoxon45}
test and Cliff's effect size\cite{Cliff93} are applied to the accuracy
and timing metrics to determine the significance of the difference
between \tool and Gitk. The Wilcoxon test is applied between commits to
determine if the size of the merge-tree effects timing and accuracy. The
null hypotheses and alternative hypotheses are stated in
Table~\ref{tab:null_alt_hypoths}.

\begin{table*}[h!]
  \centering
  \caption{Null and Alternative Hypotheses for Summarization Tasks\evan{Should I say exactly
      what the null hypotheses are referring to (counting authors,
      files, etc... or is this good enough? It's already a huge and
      redundant table) }}
  \label{tab:null_alt_hypoths}
  \begin{tabulary}{0.98\linewidth}{CCLL}
    \toprule
    Task & Metric             & Null Hypothesis                                                      & Alternative Hypothesis\\\midrule
    T4   & \tiny{Commit}      & There is no difference on accuracy or timing between \comA and \comB & There is a difference on accuracy or timing between \comA and \comB \\
    T4   & \tiny{Correctness} & \tool does not effect the correctness of the participants            & \tool does effect the correctness of the participants\\
    T4   & \tiny{Accuracy}    & There is no difference between \tool and Gitk on accuracy            & There is a difference between \tool and Gitk on accuracy\\
    T4   & \tiny{Timing}      & There is no difference between \tool and Gitk on timing              & There is a difference between \tool and Gitk on timing\\

    T5   & \tiny{Commit}      & There is no difference on accuracy or timing between \comA and \comB & There is a difference on accuracy or timing between \comA and \comB \\
    T5   & \tiny{Correctness} & \tool does not effect the correctness of the participants            & \tool does effect the correctness of the participants\\
    T5   & \tiny{Accuracy}    & There is no difference between \tool and Gitk on accuracy            & There is a difference between \tool and Gitk on accuracy\\
    T5   & \tiny{Timing}      & There is no difference between \tool and Gitk on timing              & There is a difference between \tool and Gitk on timing\\

    T6   & \tiny{Commit}      & There is no difference on accuracy or timing between \comA and \comB & There is a difference on accuracy or timing between \comA and \comB \\
    T6   & \tiny{Correctness} & \tool does not effect the correctness of the participants            & \tool does effect the correctness of the participants\\
    T6   & \tiny{Accuracy}    & There is no difference between \tool and Gitk on accuracy            & There is a difference between \tool and Gitk on accuracy\\
    T6   & \tiny{Timing}      & There is no difference between \tool and Gitk on timing              & There is a difference between \tool and Gitk on timing\\

    T7   & \tiny{Commit}      & There is no difference on accuracy or timing between \comA and \comB & There is a difference on accuracy or timing between \comA and \comB \\
    T7   & \tiny{Correctness} & \tool does not effect the correctness of the participants            & \tool does effect the correctness of the participants\\
    T7   & \tiny{Accuracy}    & There is no difference between \tool and Gitk on accuracy            & There is a difference between \tool and Gitk on accuracy\\
    T7   & \tiny{Timing}      & There is no difference between \tool and Gitk on timing              & There is a difference between \tool and Gitk on timing\\

    T8   & \tiny{Commit}      & There is no difference on accuracy or timing between \comA and \comB & There is a difference on accuracy or timing between \comA and \comB \\
    T8   & \tiny{Correctness} & \tool does not effect the correctness of the participants            & \tool does effect the correctness of the participants\\
    T8   & \tiny{Accuracy}    & There is no difference between \tool and Gitk on accuracy            & There is a difference between \tool and Gitk on accuracy\\
    T8   & \tiny{Timing}      & There is no difference between \tool and Gitk on timing              & There is a difference between \tool and Gitk on timing\\

    T9   & \tiny{Commit}      & There is no difference on accuracy or timing between \comA and \comB & There is a difference on accuracy or timing between \comA and \comB \\
    T9   & \tiny{Correctness} & \tool does not effect the correctness of the participants            & \tool does effect the correctness of the participants\\
    T9   & \tiny{Accuracy}    & There is no difference between \tool and Gitk on accuracy            & There is a difference between \tool and Gitk on accuracy\\
    T9   & \tiny{Timing}      & There is no difference between \tool and Gitk on timing              & There is a difference between \tool and Gitk on timing\\

    T10   & \tiny{Commit}      & There is no difference on accuracy or timing between \comA and \comB & There is a difference on accuracy or timing between \comA and \comB \\
    T10   & \tiny{Correctness} & \tool does not effect the correctness of the participants            & \tool does effect the correctness of the participants\\
    T10   & \tiny{Accuracy}    & There is no difference between \tool and Gitk on accuracy            & There is a difference between \tool and Gitk on accuracy\\
    T10   & \tiny{Timing}      & There is no difference between \tool and Gitk on timing              & There is a difference between \tool and Gitk on timing\\
    \bottomrule
  \end{tabulary}
\end{table*}

@@

Table~\ref{tab:cross_commit_results} shows whether the merge-tree size
has an effect on the three studied metrics. An interesting observation
from the figure is that the corrected for T5 and T9 are effected by the
size of the merge-tree, but the accuracy is not. The correctness results
for T5 and T9 are shown in Figure~\ref{fig:correctness_t5_t9}, and the
timing results for T7 are shown in Figure~\ref{fig:timing_t7}.

\begin{table}[htpb]
  \centering
  \caption{Cross-Commit Results\evan{Should I group the results by task
      or by metric? It's by metric right now}}
  \label{tab:cross_commit_results}
  \begin{tabular}{ccrl}
    \toprule
    Task & Metric      & $p$-value & Conclusion\\\midrule
    T4   & Correctness & 0.22      & Do not reject $H_0$\\
    T5   & Correctness & 0.04      & Reject $H_0$\\
    T6   & Correctness & 0.13      & Do not reject $H_0$\\
    T7   & Correctness & 0.06      & Do not reject $H_0$\\
    T8   & Correctness & 0.07      & Do not reject $H_0$\\
    T9   & Correctness & 0.04      & Reject $H_0$\\
    T10  & Correctness & 0.62      & Do not reject $H_0$\\

    T4  & Accuracy & 0.94 & Do not reject $H_0$\\
    T5  & Accuracy & 0.09 & Do not reject $H_0$\\
    T6  & Accuracy & 0.19 & Do not reject $H_0$\\
    T8  & Accuracy & 0.16 & Do not reject $H_0$\\
    T9  & Accuracy & 0.08 & Do not reject $H_0$\\
    T10 & Accuracy & 0.37 & Do not reject $H_0$\\

    T4  & Time & 0.77 & Do not reject $H_0$\\
    T5  & Time & 0.97 & Do not reject $H_0$\\
    T6  & Time & 0.90 & Do not reject $H_0$\\
    T7  & Time & 0.01 & Reject $H_0$\\
    T8  & Time & 0.87 & Do not reject $H_0$\\
    T9  & Time & 0.99 & Do not reject $H_0$\\
    T10 & Time & 0.68 & Do not reject $H_0$\\
    \bottomrule
  \end{tabular}
\end{table}

\begin{figure*}[htpb]
  \centering
  \includegraphics[width=\textwidth]{figures/userstudy/results.pdf}
  \caption{Aggregated results from the summarization tasks. The first row plots the
    correctness metric for each task. The second row plots the
    accuracy metric for each task. The third row plots the time metric
    for each task. The correctness results for T5, T9, and the timing
    results for T7 cannot be aggregated across commits, thus are
    omitted.}
  \label{fig:summarization_results}
\end{figure*}

\begin{figure*}[htpb]
  \centering

  \begin{tabular}{ m{6cm} m{6cm} }
    \includegraphics[width=6cm]{figures/userstudy/correctness/5.pdf} &
    \includegraphics[width=6cm]{figures/userstudy/correctness/9.pdf}
  \end{tabular}
  \caption{Unaggregated Correctness results for T5 and T9 \evan{Split
      this? Is it clear that between Commit 2 and Commit 1 is where the
    separation of the plots is?}}
  \label{fig:correctness_t5_t9}
\end{figure*}

\begin{figure}[htpb]
  \centering
  \includegraphics[width=0.8\linewidth]{figures/userstudy/time/7.pdf}
  \caption{Unaggregated Timing results for T7}
  \label{fig:timing_t7}
\end{figure}

\begin{table}[htpb]
  \centering
  \caption{Summarization Correctness Results}
  \label{tab:correctness_table}
  \begin{tabular}{crrc}
    \toprule
    Task                & $\chi^2$ & $p$-value & Conclusion\\\midrule
    T4                  & 13.07    & 0.0003    & Reject $H_0$\\
    \multirow{2}{*}{T5} & 5.14     & 0.0233    & Reject $H_0$\\
                        & 5.14     & 0.0233    & Reject $H_0$\\
    T6                  & 14.06    & 0.0002    & Reject $H_0$\\
    T7                  & 11.07    & 0.0009    & Reject $H_0$\\
    T8                  & 13.07    & 0.0003    & Reject $H_0$\\
    \multirow{2}{*}{T9} & 4.17     & 0.0412    & Reject $H_0$\\
                        & 6.13     & 0.0133    & Reject $H_0$\\
    T10                 & 4.00     & 0.0455    & Reject $H_0$\\
    \bottomrule
  \end{tabular}
\end{table}

Summaries for correctness, accuracy, and timing are shown in
tables~\ref{tab:correctness_table}.

@@

The full results are as follows;

@@

    T4; The $\chi^2$ statistic is $13.07$ with a p-value of $0.0003$.
    $13.07 > 3.841$ and $0.0003 < 0.05$, therefore we reject the null
    hypothesis.
    \vspace{2mm}
    \begin{tabular}{cc|rr}
      &           & \multicolumn{2}{c}{Linvis}\\
      &           & Correct                      & Incorrect\\\hline
      \multirow{2}{*}{Gitk} & Correct   & 6                            & 0\\
      & Incorrect & 15                           & 2\\
    \end{tabular}
    \vspace{3mm}

@@

    T5; The correctness results are split for this task. For \comA, the
    $\chi^2$ statistic is $5.14$ with a $p-value$ of $0.02334$. $5.14 >
    3.841$ and $0.02334 < 0.05$, therefore we reject the null
    hypothesis.
    \vspace{2mm}
    \begin{tabular}{cc|rr}
                             &           & \multicolumn{2}{c}{Linvis}\\
                             &           & Correct                      & Incorrect\\\hline
      \multirow{2}{*}{Gitk}  & Correct   & 4                            & 0\\
                             & Incorrect & 7                            & 0\\
    \end{tabular}
    \vspace{3mm}

    The $\chi^2$ statistic for \comB is $5.14$ with a p-value of
    $0.02334$. $4.14 > 3.841$ and $0.02334 < 0.05$, therefore we reject
    the null hypothesis.
    \vspace{2mm}
    \begin{tabular}{cc|rr}
                             &           & \multicolumn{2}{c}{Linvis}\\
                             &           & Correct                      & Incorrect\\\hline
      \multirow{2}{*}{Gitk}  & Correct   & 1                            & 0\\
                             & Incorrect & 7                            & 4\\
    \end{tabular}
    \vspace{3mm}

@@

    T9; The correctness results are split for this task. For \comA, the
    $\chi^2$ statistic is $4.17$ with a p-value of $0.0412$. $4.17 >
    3.841$ and $0.0412 < 0.05$, therefore we reject the null hypothesis.
    \vspace{2mm}
    \begin{tabular}{cc|rr}
                             &           & \multicolumn{2}{c}{Linvis}\\
                             &           & Correct                      & Incorrect\\\hline
      \multirow{2}{*}{Gitk}  & Correct   & 5                            & 0\\
                             & Incorrect & 6                            & 0\\
    \end{tabular}
    \vspace{3mm}

    The $\chi^2$ statistic for \comB is $6.125$ with a p-value of
    $0.0133$. $6.125 > 3.841$ and $0.0133 < 0.05$, therefore we reject
    the null hypothesis.
    \vspace{2mm}
    \begin{tabular}{cc|rr}
                             &           & \multicolumn{2}{c}{Linvis}\\
                             &           & Correct                      & Incorrect\\\hline
      \multirow{2}{*}{Gitk}  & Correct   & 1                            & 0\\
                             & Incorrect & 8                            & 3\\
    \end{tabular}
    \vspace{3mm}
